%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
%\addbibresource{bibliography.bib}

\begin{document}
\header{Devang}{Bacharwar}
       {Computer Science and Engineering, IIT Mandi}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    109, B1, Parashar Hostel, Kamand
    IIT Mandi
    Mandi, India
    ~
    \href{mailto:devang.bacharwar@gmail.com}{devang.bacharwar@ gmail.com}
    {+91-9816111283}
%    \href{http://friggeri.net}{http://friggeri.net}
    \href{https://github.com/devangb}{github: devangb}
    \href{https://in.linkedin.com/in/devangb}{linkedin: devangb}
  \section{programming}
    Proficient: C++, C, Python, Ruby
    Basic: PHP, Javascript, Bash
  \section{frameworks}
  	Rails
  \section{development tools}
  	Vim, Linux, Sublime text, Git, NaturalDocs
\end{aside}


\section{Education}

\begin{entrylist}
  \entry
    {since 2012}
    {B. Tech. {\normalfont Computer Science and Engineering}}
    {Indian Institute of Technology, Mandi}
    {CGPA - 7.86{\small (till VI\textsuperscript{th} Semester)}}
  \entry
    {2012}
    {XII\textsuperscript{th} Std.}
    {John Milton Public School, Agra}
    {Percentage - 84.6\%}
  \entry
    {2010}
    {X\textsuperscript{th} Std.}
    {St. John's Sr. Sec. School, Firozabad}
    {GPA - 9.2}
\end{entrylist}

\section{Internships}
\begin{entrylist}
  \internentry
    {05-08 2015}
    {Google Summer of Code 2015}
    {\href{http://stellar.cct.lsu.edu/}{The STE||AR Group}}
    {\emph{Application/Counter CSV files for HPX}}
    {Implemented the collection of performance counters and generating CSV files for performance counter data of HPX, a high performance C++ runtime. This is now helping in analysing the performance of HPX using data precessing tools}
%  \internentry
%  	{07-08 2014}
%  	{Internship at M2C Solutions}
%  	{\href{http://m2ccraft.com/}{M2C crafts}}
%  	{\emph{Android application for onsite restaurant reviews}}
%  	{Contributed in development of an Android Application for restaurant search and
%on-site review.}  	
\end{entrylist}

\section{Projects}
\begin{entrylist}
  \projectentry
    {08-11 2013}
    {G-read Book recommender}
    {Database Practicum}
    {\emph{Book rating, review and recommendation application developed under guidance of Dr. Sukumar Bhattacharya.}}
    {A book recommendation web application implemented using Rails framework and postgreSQL. Application lets users rate and review books and get book recommendations. It also lets them follow other users and get feed based on their activity.}
  \projectentry
    {02-06 2014}
    {Autonomous Garbage collection bot}
    {Design Practicum}
    {\emph{Project done under Dr. Rajeev Kumar and Dr. Ajay Soni.}}
    {This project won first prize in openhouse. An autonomous garbage collecting bot developed for the purpose of cleaning parks and beaches. It used color deduction and edge detection algorithms running on raspberry pi for detecting garbage in uniform background.}
  \projectentry
    {11-12 2013}
    {Donate}
    {Inter-IIT Techmeet, IIT Bombay}
    {\emph{Application to track and index donation of things.}}
    {A web application developed for maintaining a database of donors and seekers implemented using Rails and SQLite, which can be used for different types of commodities.}
  \projectentry
  	{08 2015}
  	{Machine Learning algorithms library for Apache Flink}
  	{Major Technical Project}
  	{\emph{Project aims at implementing Machine learning algorithm libraries for Apache Flink under guidance of Dr. Arti Kashyap}}
  	{Apache Flink is an open source platform for scalable batch and stream data processing. Flink is targeting machine learning aggressively. This project aims to contribute to Apache FlinkML.}
\end{entrylist}

\section{Workshops}
\begin{entrylist}
  \projectentry
  	{01 2015}
  	{MIT Media lab Design Innovation Workshop}
  	{Immersive Storytelling track}
  	{\emph{Let's stop drugs} - \emph{Project aimed at providing a virtual experience of a LSD drug trip}}
  	{The workshop aimed at providing new interfaces and experiences in the field of immersive storytelling. The project Let's stop drug used Google cardboard with android application recreating the visual experience of LSD trip.}
\end{entrylist}

%\section{Research projects, papers published and patents}
%\begin{entrylist}
%  \projectentry
%    {08-11 2013}
%    {Light in Shadow}
%    {Inter-IIT Techmeet, IIT Kanpur}
%    {\emph{Project to provide a energy efficient lighting solution mainly focused for slum areas.}}
%    {An open source lighting solution using the bleach water bottle and LED assembly as a potential  replacement for Electric Bulbs. It uses LEDs , solar panel and an LDR circuit which provides light for illuminating the bleach water bottle during night, which is done by sunlight during daytime.}
%\end{entrylist}

\section{Courses}
\begin{entrylist}
  \courseentry
  	{II\textsuperscript{nd} Semester}
  	{Computation for Engineers, Linear Algebra}
  \courseentry
  	{III\textsuperscript{rd} Semester}
  	{Data structures and Algorithms, Mathematical Foundation for Computer Science, Database Practicum}
  \courseentry
  	{IV\textsuperscript{th} Semester}
  	{Advanced Data Structures and Algorithms, Design Practicum}
  \courseentry
  	{V\textsuperscript{th} Semester}
  	{Computer Organization, Paradigms of Programming, Systems Practicum, Formal Languages and Automata Theory, Computational Financial Modelling, Software Engineering}
  \courseentry
  	{VI\textsuperscript{th} Semester}
  	{Design of Concurrent Softwares, Information and Database Systems, Communication of Distributed Processes, Large Applications Practicum, Algorithm Design and Analysis}
  \courseentry
  	{VII\textsuperscript{th} Semester}
  	{Pattern Recognition, Digital Image Processing, Data Mining for Decision Making}
\end{entrylist}

\section{Position of responsibility}

\begin{entrylist}
  \responsibilityentry
  	{2014-15}
  	{\emph{Coordinator, Programme Management Club.}}
  \responsibilityentry
  	{02-06 2014}
  	{\emph{Team Coordinator, Design Practicum.}}
  \responsibilityentry
  	{2013-14}
  	{\emph{Control and Management Coordinator, Exodia’14, IIT Mandi’s Techno-Cult fest.}}
  \responsibilityentry
  	{2013-14}
  	{\emph{Coordinator, Debating Society.}}
\end{entrylist}

\section{Scholarships, Awards and Achievements}

\begin{entrylist}
  \awardentry
   	{2013-2015}
   	{Represented IIT Mandi at Inter-IIT Techmeet for three consecutive years \emph{[IIT Kanpur(2013), IIT Bombay(2014), IIT Kharagpur(2015)]}}
  \awardentry
  	{05 2014}
  	{I\textsuperscript{st} prize in Design Practicum.}
  \awardentry
  	{10 2013}
  	{III\textsuperscript{rd} prize in National competition Manthan organised by CAG}
\end{entrylist}

\section{Extracurricular activities}
\begin{entrylist}
  \responsibilityentry
  	{}
  	{Active member of literary society.}
  \responsibilityentry
  	{}
  	{Active member of Programming club, ACM student chapter, Energy club.}
  \responsibilityentry
  	{}
  	{Active member of Programme management group, Art geeks.}
\end{entrylist}

%\section{Reference and Recommendations}

%\section{publications}


%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
